Gafo-cc data processing

### 2024-01-29 analysis/gafo-cc-data-processing.Rmd
prep merge

unique(tidy_data_namibia$subjID)
```

@@

tidy_demographics_namibia <- raw_demographics_namibia %>% 
  rename(subjID = ID)%>%
  left_join(testdates)%>%
  mutate(
    ageInYears = as.numeric(difftime(test_date,BirthDate, units = "days")/365.25),
  ) %>%
  select(-c(`First Name`, Name, BirthDate, TestDate,test_date, Comment))%>% 
  rename_all(tolower)%>%
  filter(!is.na(ageinyears))

@@

```{r}
data_namibia <- tidy_demographics_namibia%>%
  left_join(tidy_data_namibia%>%rename_all(tolower),by = c("subjid"))%>%
  distinct(subjid, trialnr, .keep_all = T)

@@

```{r}
data_namibia%>%
  filter(community == "windhoek")%>%
  mutate(age_group = substr(ageinyears, 1,1))%>%
  #group_by(age_group)%>%
  summarise(n = n_distinct(subjid))

data_namibia%>%
  filter(community == "windhoek")%>%
  group_by(ageinyears)%>%
  summarise(n= n_distinct(subjid))%>%
  ggplot(aes(x = ageinyears, y = ""))+
  geom_count(alpha = .5)+
  xlim(2.5, 8)+
  theme_bw()
```

@@

@@

```{r}
tidy_demographics_leipzig%>%
  filter(!subjid %in% tidy_data_leipzig$subjID)
```

```{r}
data_leipzig <- tidy_demographics_leipzig%>%
  left_join(tidy_data_leipzig%>%rename_all(tolower),by = c("subjid"))%>%
  distinct(subjid, trialnr, .keep_all = TRUE)

```{r}
data_leipzig%>%
  group_by(subjid)%>%
  summarise(n())

data_leipzig%>%
  #group_by(subjid)%>%
  summarise(n = n_distinct(subjid))

data_leipzig%>%
  mutate(age_group = substr(ageinyears, 1, 1))%>%
  select(subjid, sex, age_group, screen, touchscreen, household, children, younger_children)%>%
  na.omit()%>%
  group_by(age_group, sex)%>%
  summarise(n = n_distinct(subjid))

data_leipzig%>%
  mutate(age_group = substr(ageinyears, 1, 1))%>%
  select(subjid, sex, age_group, screen, touchscreen, household, children, younger_children)%>%
  na.omit()%>%
  group_by(age_group)%>%
  summarise(n = n_distinct(subjid))
```

@@

@@

```{r}
data_nigeria <- tidy_demographics_nigeria%>%
  left_join(tidy_data_nigeria%>%rename_all(tolower),by = c("subjid"))%>%
  mutate(location = community,
         community = "akure")%>%
  distinct(subjid, trialnr, .keep_all = TRUE)
```

@@

```{r}
tidy_data_zambia%>%
  summarise(n = n_distinct(subjID))
```

@@

@@

@@

```{r}
data_stanford <- read.csv("../../raw_data/gafo-cc/stanford/tidy_data_extra.csv")%>%
  mutate(subjID = paste0("S",subjID),
         community = "stanford",
         screen = ifelse(screen == "yes", 1, 0),
         touchscreen = ifelse(touchscreen == "yes", 1, 0),
         browserVersion = factor(browserVersion),
         targetPosition = factor(targetPosition))%>%
  select(-touchScreen)%>%
  rename(ageinyears = age)%>%
  rename_all(tolower)%>%
  distinct(subjid, trialnr, .keep_all = T)
```

```{r}
data_stanford%>%
  mutate(age_group = substr(ageinyears, 1,1))%>%
  group_by(age_group)%>%
  summarise(n = n_distinct(subjid))

@@

@@

unique(raw_data_plymouth$subjID)
```

```{r}
tidy_data_plymouth%>%
  filter(trialType == "test")%>%
  group_by(subjID)%>%
  summarise(n = n())

tidy_data_plymouth%>%
  filter(trialType == "test")%>%
  summarise(n = n_distinct(subjID))

tidy_data_plymouth%>%
  filter(subjID == "uksch002")
```

```{r demographics}
raw_demographics_plymouth <- bind_rows(
  read_xlsx("../../raw_data/gafo-cc/plymouth/participants_information_updated_2023_May.xlsx", sheet = 1)
  )%>%
  filter(tested == "yes")

@@

```{r}
data_plymouth <- tidy_demographics_plymouth%>%
  left_join(tidy_data_plymouth%>%rename_all(tolower),by = c("subjid"))%>%
  distinct(subjid, trialnr, .keep_all = TRUE)

data_plymouth%>%
  #mutate(age_group = substr(ageinyears, 1,1))%>%
  #group_by(age)%>%
  summarise(n = n_distinct(subjid))

data_plymouth%>%
  group_by(age)%>%
  summarise(n())

 data_plymouth%>%
   filter(is.na(durationanimationballoontotal))
```

@@

```{r}
tidy_data_mex%>%
  summarise(n = n_distinct(subjID))
```

```{r demographics}
raw_demographics_mex <- bind_rows(
  read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/mexico/participants.xlsx", sheet = 1)
  )%>%
  filter(!is.na(lastname))%>%
  mutate(birth_date = ifelse(birth_date == 29042017, 20170429, birth_date))

@@

    test_date = as.Date(as.character(test_date), format = "%Y%m%d"),
    birth_date = as.Date(as.character(birth_date), format = "%Y%m%d"),
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
  )  %>%
  select(-c(name, lastname, test_date, birth_date, comment))%>%
  filter(!is.na(ageinyears))

@@

```{r}
data_mex <- tidy_demographics_mex%>%
  left_join(tidy_data_mex%>%rename_all(tolower),by = c("subjid"))%>%
  mutate(community = "mexico")%>%
  distinct(subjid, trialnr, .keep_all = TRUE)

data_mex%>%summarise(n = n_distinct(subjid))

```
```{r}
# data_liz <- bind_rows(data_mex%>%
#   filter(trialtype == "test", voiceover == F)%>%
#   mutate(click_distance = abs(clickdistfromtargetcenterx))%>%
#   select("subjid" ,"community" ,"ageinyears" , "trialnr", "targetposition",  "click_distance", "sex", "economical_activity_dad" , "economical_activity_mom"   ,    "parents_education_level_dad"  , "parents_education_level_mom" ,  "income" ,    "screen"           ,             "touchscreen"       ,            "household"     ,                "children" ,
#         "younger_children"),
# 
# data_leipzig%>%
#   filter(trialtype == "test", voiceover == F)%>%
#   mutate(click_distance = abs(clickdistfromtargetcenterx))%>%
#   select("subjid" ,"community" ,"ageinyears" , "trialnr", "targetposition",  "click_distance", "sex", "screen"           ,             "touchscreen"       ,            "household"     ,                "children" ,
#         "younger_children")
# )
# 
# 
#   write_csv(data_liz, "../data/gafo-cc-data-lizbeth.csv")
#   
# 
# data_liz <- read_csv("gafo-cc-data-lizbeth.csv")
# 
# 
# data_liz_agg <- data_liz%>%
#   group_by(subjid, community, ageinyears, sex, economical_activity_dad, economical_activity_mom, parents_education_level_dad, parents_education_level_mom, income, screen, touchscreen, household, children, younger_children)%>%
#   summarise(mean_distance = mean(click_distance))%>% # aggregate data to get average click distance
#   ungroup()%>%
#   mutate(mean_distance_scale = scale(mean_distance, scale = F, center = T), # make the DV so that it has a mean of 0
#          z_ageinyears = scale(ageinyears, scale = F, center = T), # scale numeric variables
#          f_income = factor(income),# convert numeric variable into a factor because different values represent different categories
#          z_household = scale(household)) 
# 
# 
# library(lme4)
# 
# m1 <- lm(mean_distance_scale ~ z_ageinyears + community, data = data_liz_agg)
# 
# drop1(m1, test = "Chisq") # to get p-values for entire factors you need to use drop1
# 
# summary(m1)
```

@@

#unique(tidy_data_leipzig$subjID)

tidy_data_china%>%
  filter(subjID == "china077")

n_distinct(tidy_data_china$subjID)

tidy_data_china%>%
  group_by(subjID)%>%
  summarise(n())
```

@@

tidy_demographics_china%>%
  arrange(ageinyears)
```

```{r}
data_china <- tidy_demographics_china%>%
  left_join(tidy_data_china%>%rename_all(tolower),by = c("subjid"))%>%
  distinct(subjid, trialnr, .keep_all = TRUE)

data_china%>%
  #mutate(age_group = substr(ageinyears, 1,1))%>%
  #group_by(age_group)%>%
  summarise(n = n_distinct(subjid))

data_china%>%
  group_by(subjid)%>%
  summarise(n())

@@

@@

```{r}
tidy_data_arg%>%
  summarise(n = n_distinct(subjID))

tidy_data_arg%>%
  group_by(subjID)%>%
  summarise(n = n())
```

@@

tidy_demographics_arg%>%
  filter(ageinyears < 2)
```

```{r}
raw_demographics_arg%>%
  filter(!id %in% tidy_data_arg$subjID)

tidy_data_arg%>%
  filter(!subjID %in% raw_demographics_arg$id)
```

```{r}
data_arg <- tidy_demographics_arg%>%
  left_join(tidy_data_arg%>%rename_all(tolower),by = c("subjid"))%>%
  mutate(community = "buenos_aires")%>%
  distinct(subjid, trialnr, .keep_all = TRUE)

data_arg%>%
  group_by(community)%>%
  summarise(n = n_distinct(subjid))

data_arg%>%
  group_by(subjid)%>%
  summarise(n = n())
```

@@

```{r}
tidy_data_ind%>%
  summarise(n = n_distinct(subjID))

tidy_data_ind%>%
  group_by(subjID)%>%
  summarise(n = n())

@@

```{r }
raw_demographics_ind <- read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/india/gafo-cc-india-participants.xlsx", sheet = 1)

tidy_demographics_ind <- raw_demographics_ind %>% 
  mutate(
    test_date = as.Date(as.character(test_date), format = "%Y%m%d"),
    birth_date = as.Date(as.character(birth_date), format = "%Y%m%d"),
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
  )  %>%
  select(-c(first_name, last_name, test_date, birth_date, comment))%>%
  filter(!is.na(ageinyears))%>%
  rename(subjid = id)

@@

```{r}
data_ind <- tidy_demographics_ind%>%
  left_join(tidy_data_ind%>%rename_all(tolower),by = c("subjid"))%>%
  mutate(community = "india")%>%
  distinct(subjid, trialnr, .keep_all = TRUE)

data_ind%>%
  group_by(subjid)%>%
  summarise(n = n())

@@

@@

```{r}
tidy_data_nz%>%
  #filter(trialType == "test")%>%
  group_by(subjID)%>%
  summarise(n = n())

tidy_data_nz%>%
  filter(trialType == "test")%>%
  summarise(n = n_distinct(subjID))

tidy_data_nz%>%
  filter(subjID == "uksch002")
```

```{r demographics}
raw_demographics_nz <- bind_rows(
  read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/new_zealand/gafo-cc-new-zealand-participants.xlsx", sheet = 1)
  )

@@

```{r}
data_nz <- tidy_demographics_nz%>%
  filter(subjid != "NZ000001")%>%
  left_join(tidy_data_nz%>%rename_all(tolower),by = c("subjid"))%>%
  distinct(subjid, trialnr, .keep_all = TRUE)

data_nz%>%
  #mutate(age_group = substr(ageinyears, 1,1))%>%
  #group_by(age)%>%
  summarise(n = n_distinct(subjid))

# data_nz%>%
#   group_by(age)%>%
#   summarise(n())
```

@@

```{r}
tidy_data_tur%>%
  summarise(n = n_distinct(subjID))

tidy_data_tur%>%
  group_by(subjID)%>%
  summarise(n = n())

unique(tidy_data_tur$subjID)
```

@@

```{r}
data_tur <- tidy_demographics_tur%>%
  left_join(tidy_data_tur%>%rename_all(tolower),by = c("subjid"))%>%
  mutate(community = "turkey")%>%
  distinct(subjid, trialnr, .keep_all = TRUE)%>%
  mutate(subjid = recode(subjid, 
                     "EBRAR100" = "TUR00001",
                     "FATMA400" = "TUR00002",
                     "ASYAA200" = "TUR00003"))

data_tur%>%
  group_by(subjid)%>%
  summarise(n = n())

data_tur%>%
  mutate(age_group = substr(ageinyears, 1,1))%>%
  group_by(age_group)%>%
  summarise(n = n_distinct(subjid))

>>>>

```{r}
# quality checks

# range of click distance: min = 0; max = 1920
range(abs(tidy_data_namibia$clickDistFromTargetCenterX)) #

# number of trials: everyone should have more than 4 trials.
tidy_data_namibia%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)

@@

tidy_demographics_namibia <- raw_demographics_namibia %>% 
  rename(subjID = ID)%>%
  left_join(testdates)%>%
  mutate(
    ageInYears = as.numeric(difftime(test_date,BirthDate, units = "days")/365.25),
    Children = ifelse(subjID == "W0000023", 2, Children)
  ) %>%
  select(-c(`First Name`, Name, BirthDate, TestDate,test_date, Comment))%>% 
  rename_all(tolower)%>%
  filter(!is.na(ageinyears))

@@

```{r}
# quality checks

# check for typos in subject names, is there a data file for every child in the demographics spreadsheet?
tidy_demographics_namibia%>%
  filter(!subjid %in% tidy_data_namibia$subjID)

# range of ages: should not be below 2.5
range(tidy_demographics_namibia$ageinyears)

# screen and touchscreen should only be 0 or 1 
unique(tidy_demographics_namibia$screen) 
unique(tidy_demographics_namibia$touchscreen)

# children should at least be 1 (the tested child) 
tidy_demographics_namibia%>%filter(children < 1)
# household should at least be 2 (the tested child and one adult) 
tidy_demographics_namibia%>%filter(household < 2) 
# household should be larger than children
tidy_demographics_namibia%>%filter(children >= household) 
# youngerchildren should be fewer than children
tidy_demographics_namibia%>%filter(youngerchildren >= children)

exclude_namib <- tidy_demographics_namibia%>%filter(children >= household) %>% pull(subjid)

@@

```{r}
data_namibia <- tidy_demographics_namibia%>%
  left_join(tidy_data_namibia%>%rename_all(tolower),by = c("subjid"))%>%
  filter(!subjid %in% exclude_namib)%>%
  distinct(subjid, trialnr, .keep_all = T)

```{r}
# did a child get lost on the way?
n_distinct(tidy_demographics_namibia$subjid) == (n_distinct(data_namibia$subjid) + length(exclude_namib))
```

@@

```{r}
# quality checks

# range of click distance: min = 0; max = 1920
range(abs(tidy_data_leipzig$clickDistFromTargetCenterX)) #

# number of trials: everyone should have more than 4 trials.
tidy_data_leipzig%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)

@@

```{r}
# quality checks

# check for typos in subject names
tidy_demographics_leipzig%>%
  filter(!subjid %in% tidy_data_leipzig$subjID)

# range of ages: should not be below 2.5
range(tidy_demographics_leipzig$ageinyears)

# screen and touchscreen should only be 0 or 1 or NA
unique(tidy_demographics_leipzig$screen) 
unique(tidy_demographics_leipzig$touchscreen)

# children should at least be 1 (the tested child) 
tidy_demographics_leipzig%>%filter(children < 1)
# household should at least be 2 (the tested child and one adult) 
tidy_demographics_leipzig%>%filter(household < 2) 
# household should be larger than children
tidy_demographics_leipzig%>%filter(children >= household) 
# youngerchildren should be fewer than children
tidy_demographics_leipzig%>%filter(younger_children >= children) 
```

```{r}
data_leipzig <- tidy_demographics_leipzig%>%
  left_join(tidy_data_leipzig%>%rename_all(tolower),by = c("subjid"))%>%
  distinct(subjid, trialnr, .keep_all = TRUE)
```

```{r}
# did a child get lost on the way?
n_distinct(tidy_demographics_leipzig$subjid) <= (n_distinct(tidy_data_leipzig$subjID))
```

@@

```{r}
# quality checks

# range of click distance: min = 0; max = 1920
range(abs(tidy_data_nigeria$clickDistFromTargetCenterX)) #

# number of trials: everyone should have more than 4 trials.
tidy_data_nigeria%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)

@@

```{r}
# quality checks

# check for typos in subject names
tidy_demographics_nigeria%>%
  filter(!subjid %in% tidy_data_nigeria$subjID)

# range of ages: should not be below 2.5
range(tidy_demographics_nigeria$ageinyears)

# screen and touchscreen should only be 0 or 1 or NA
unique(tidy_demographics_nigeria$screen) 
unique(tidy_demographics_nigeria$touchscreen)

# children should at least be 1 (the tested child) 
tidy_demographics_nigeria%>%filter(children < 1)
# household should at least be 2 (the tested child and one adult) 
tidy_demographics_nigeria%>%filter(household < 2) 
# household should be larger than children
tidy_demographics_nigeria%>%filter(children >= household) 
# younger children should be fewer than children
tidy_demographics_nigeria%>%filter(younger_children >= children)

exclude_niger <- tidy_demographics_nigeria%>%filter(younger_children >= children) %>% pull(subjid)
```

```{r}
data_nigeria <- tidy_demographics_nigeria%>%
  left_join(tidy_data_nigeria%>%rename_all(tolower),by = c("subjid"))%>%
  filter(!subjid %in% exclude_niger)%>%
  mutate(location = community,
         community = "akure")%>%
  distinct(subjid, trialnr, .keep_all = TRUE)
```

```{r}
# did a child get lost on the way?
n_distinct(tidy_demographics_nigeria$subjid) == (n_distinct(data_nigeria$subjid) + length(exclude_niger))
```

@@

```{r}
# quality checks

# range of click distance: min = 0; max = 1920
range(abs(tidy_data_zambia$clickDistFromTargetCenterX)) #

# number of trials: everyone should have more than 4 trials.
tidy_data_zambia%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)

@@

```{r}
# quality checks

# check for typos in subject names
tidy_demographics_zambia%>%
  filter(!subjid %in% tidy_data_zambia$subjID)

# range of ages: should not be below 2.5
range(tidy_demographics_zambia$ageinyears)

# screen and touchscreen should only be 0 or 1 or NA
unique(tidy_demographics_zambia$screen) 
unique(tidy_demographics_zambia$touchscreen)

# children should at least be 1 (the tested child) 
tidy_demographics_zambia%>%filter(children < 1)
# household should at least be 2 (the tested child and one adult) 
tidy_demographics_zambia%>%filter(household < 2) 
# household should be larger than children
tidy_demographics_zambia%>%filter(children >= household) 
# younger children should be fewer than children
tidy_demographics_zambia%>%filter(younger_children >= children) 
```

@@

```{r}
# did a child get lost on the way?
n_distinct(tidy_demographics_zambia$subjid) <= (n_distinct(data_zambia$subjid))
```

@@

```{r}
raw_data_stanford <- read.csv("../../raw_data/gafo-cc/stanford/tidy_data_extra.csv")%>%
  mutate(subjID = paste0("S",subjID),
         community = "stanford",
         screen = ifelse(screen == "yes", 1, 0),
         touchscreen = ifelse(touchscreen == "yes", 1, 0),
         browserVersion = factor(browserVersion),
         targetPosition = factor(targetPosition))%>%
  select(-touchScreen)%>%
  rename(ageinyears = age)%>%
  rename_all(tolower)%>%
  distinct(subjid, trialnr, .keep_all = T)
```

```{r}
# quality checks

# range of click distance: min = 0; max = 1920
range(abs(raw_data_stanford$clickdistfromtargetcenterx)) #

# number of trials: everyone should have more than 4 trials.
raw_data_stanford%>%group_by(subjid)%>%filter(voiceover == F, trialtype == "test")%>%summarise(n = n())%>%filter(n<5)

@@

```{r}
# quality checks

# range of ages: should not be below 2.5
range(raw_data_stanford$ageinyears)

# screen and touchscreen should only be 0 or 1 or NA
unique(raw_data_stanford$screen) 
unique(raw_data_stanford$touchscreen)

# children should at least be 1 (the tested child) 
raw_data_stanford%>%filter(children < 1)
# household should at least be 2 (the tested child and one adult) 
raw_data_stanford%>%filter(household < 2) 
# household should be larger than children
raw_data_stanford%>%filter(children >= household) 
# youngerchildren should be fewer than children
raw_data_stanford%>%filter(younger_children >= children)

exclude_stanf <- raw_data_stanford%>%filter(children >= household)%>%distinct(subjid)%>%pull(subjid)
```

```{r}
data_stanford <- raw_data_stanford%>%
  filter(!subjid %in% exclude_stanf)
```

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali")
  ) %>%
  mutate(subjID = ifelse(grepl("2023-03-11T19:4", timestamp) & subjID == "uksch048", "uksch049", subjID),
         subjID = ifelse(subjID == "Uksch002", "uksch002", subjID),
         subjID = ifelse(subjID == "Uksch003", "uksch003", subjID))%>%
  mutate(subjID =as.factor(subjID))%>%
  select(-touchScreen)%>%
  mutate_if(is.character, as.factor)%>% 
  distinct(subjID, trialNr, .keep_all = T)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
```

```{r}
# quality checks

# range of click distance: min = 0; max = 1920
range(abs(tidy_data_plymouth$clickDistFromTargetCenterX)) #

# number of trials: everyone should have more than 4 trials.
tidy_data_plymouth%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)

```{r demographics}
raw_demographics_plymouth <- bind_rows(
  read_xlsx("../../raw_data/gafo-cc/plymouth/participants_information_updated_2023_May.xlsx", sheet = 1)
  )%>%
  filter(tested == "yes", subjid != "uksch057")

@@

```{r}
# quality checks

# check for typos in subject names
tidy_demographics_plymouth%>%
  filter(!subjid %in% tidy_data_plymouth$subjID)

# range of ages: should not be below 2.5
range(tidy_demographics_plymouth$ageinyears)

# screen and touchscreen should only be 0 or 1 or NA
unique(tidy_demographics_plymouth$screen) 
unique(tidy_demographics_plymouth$touchscreen)

# children should at least be 1 (the tested child) 
tidy_demographics_plymouth%>%filter(children < 1)
# household should at least be 2 (the tested child and one adult) 
tidy_demographics_plymouth%>%filter(household < 2) 
# household should be larger than children
tidy_demographics_plymouth%>%filter(children >= household) 
# youngerchildren should be fewer than children
tidy_demographics_plymouth%>%filter(younger_children >= children) 
```

```{r}
data_plymouth <- tidy_demographics_plymouth%>%
  left_join(tidy_data_plymouth%>%rename_all(tolower),by = c("subjid"))%>%
  distinct(subjid, trialnr, .keep_all = TRUE)
```

@@

```{r}
# quality checks

# range of click distance: min = 0; max = 1920
range(abs(tidy_data_mex$clickDistFromTargetCenterX)) #

# number of trials: everyone should have more than 4 trials.
tidy_data_mex%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)

```{r demographics}
raw_demographics_mex <- bind_rows(
  read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/mexico/participants.xlsx", sheet = 1)
  )%>%
  filter(!is.na(lastname))%>%
  mutate(birth_date = ifelse(birth_date == 29042017, 20170429, birth_date), 
         subjid = ifelse(subjid == "Mexva37", "Mexva037", subjid),
         subjid = ifelse(subjid == "Mexva51", "Mexva051", subjid), 
         children = ifelse(subjid == "Mexli040", children + 1, children),
         children = ifelse(subjid == "Mexli064", children + 1, children))

@@

    test_date = as.Date(as.character(test_date), format = "%Y%m%d"),
    birth_date = as.Date(as.character(birth_date), format = "%Y%m%d"),
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
  )  %>%
  select(-c(name, lastname, test_date, birth_date, comment))%>%
  filter(!is.na(ageinyears))%>%
  mutate(household = household + children)

@@

```{r}
# quality checks

# check for typos in subject names
tidy_demographics_mex%>%
  filter(!subjid %in% tidy_data_mex$subjID)

# range of ages: should not be below 2.5
range(tidy_demographics_mex$ageinyears)

# screen and touchscreen should only be 0 or 1 or NA
unique(tidy_demographics_mex$screen) 
unique(tidy_demographics_mex$touchscreen)

# children should at least be 1 (the tested child) 
tidy_demographics_mex%>%filter(children < 1)
# household should at least be 2 (the tested child and one adult) 
tidy_demographics_mex%>%filter(household < 2) 
# household should be larger than children
tidy_demographics_mex%>%filter(children >= household) 
# youngerchildren should be fewer than children
tidy_demographics_mex%>%filter(younger_children >= children) 
```

```{r}
data_mex <- tidy_demographics_mex%>%
  left_join(tidy_data_mex%>%rename_all(tolower),by = c("subjid"))%>%
  mutate(community = "mexico")%>%
  distinct(subjid, trialnr, .keep_all = TRUE)
```

```{r}
# data_liz <- bind_rows(data_mex%>%
#   filter(trialtype == "test", voiceover == F)%>%
#   mutate(click_distance = abs(clickdistfromtargetcenterx))%>%
#   select("subjid" ,"community" ,"ageinyears" , "trialnr", "targetposition",  "click_distance", "sex", "economical_activity_dad" , "economical_activity_mom"   ,    "parents_education_level_dad"  , "parents_education_level_mom" ,  "income" ,    "screen"           ,             "touchscreen"       ,            "household"     ,                "children" ,
#         "younger_children"),
# 
# data_leipzig%>%
#   filter(trialtype == "test", voiceover == F)%>%
#   mutate(click_distance = abs(clickdistfromtargetcenterx))%>%
#   select("subjid" ,"community" ,"ageinyears" , "trialnr", "targetposition",  "click_distance", "sex", "screen"           ,             "touchscreen"       ,            "household"     ,                "children" ,
#         "younger_children")
# )
# 
# 
#   write_csv(data_liz, "../data/gafo-cc-data-lizbeth.csv")
#   
# 
# data_liz <- read_csv("gafo-cc-data-lizbeth.csv")
# 
# 
# data_liz_agg <- data_liz%>%
#   group_by(subjid, community, ageinyears, sex, economical_activity_dad, economical_activity_mom, parents_education_level_dad, parents_education_level_mom, income, screen, touchscreen, household, children, younger_children)%>%
#   summarise(mean_distance = mean(click_distance))%>% # aggregate data to get average click distance
#   ungroup()%>%
#   mutate(mean_distance_scale = scale(mean_distance, scale = F, center = T), # make the DV so that it has a mean of 0
#          z_ageinyears = scale(ageinyears, scale = F, center = T), # scale numeric variables
#          f_income = factor(income),# convert numeric variable into a factor because different values represent different categories
#          z_household = scale(household)) 
# 
# 
# library(lme4)
# 
# m1 <- lm(mean_distance_scale ~ z_ageinyears + community, data = data_liz_agg)
# 
# drop1(m1, test = "Chisq") # to get p-values for entire factors you need to use drop1
# 
# summary(m1)
```

@@

```{r}
# quality checks

# range of click distance: min = 0; max = 1920
range(abs(tidy_data_china$clickDistFromTargetCenterX)) #

# number of trials: everyone should have more than 4 trials.
tidy_data_china%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)

@@

@@

```{r}
# quality checks

# check for typos in subject names
tidy_demographics_china%>%
  filter(!subjid %in% tidy_data_china$subjID)

# range of ages: should not be below 2.5
range(tidy_demographics_china$ageinyears)

# screen and touchscreen should only be 0 or 1 or NA
unique(tidy_demographics_china$screen) 
unique(tidy_demographics_china$touchscreen)

# children should at least be 1 (the tested child) 
tidy_demographics_china%>%filter(children < 1)
# household should at least be 2 (the tested child and one adult) 
tidy_demographics_china%>%filter(household < 2) 
# household should be larger than children
tidy_demographics_china%>%filter(children >= household) 
# youngerchildren should be fewer than children
tidy_demographics_china%>%filter(younger_children >= children) 
```

```{r}
data_china <- tidy_demographics_china%>%
  left_join(tidy_data_china%>%rename_all(tolower),by = c("subjid"))%>%
  distinct(subjid, trialnr, .keep_all = TRUE)
```

@@

```{r}
# quality checks

# range of click distance: min = 0; max = 1920
range(abs(tidy_data_arg$clickDistFromTargetCenterX)) #

# number of trials: everyone should have more than 4 trials.
tidy_data_arg%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)

@@

```{r}
# quality checks

# check for typos in subject names
tidy_demographics_arg%>%
  filter(!subjid %in% tidy_data_arg$subjID)

# range of ages: should not be below 2.5
range(tidy_demographics_arg$ageinyears)

# screen and touchscreen should only be 0 or 1 or NA
unique(tidy_demographics_arg$screen) 
unique(tidy_demographics_arg$touchscreen)

# children should at least be 1 (the tested child) 
tidy_demographics_arg%>%filter(children < 1)
# household should at least be 2 (the tested child and one adult) 
tidy_demographics_arg%>%filter(household < 2) 
# household should be larger than children
tidy_demographics_arg%>%filter(children >= household) 
# youngerchildren should be fewer than children
tidy_demographics_arg%>%filter(younger_children >= children) 
```

```{r}
data_arg <- tidy_demographics_arg%>%
  left_join(tidy_data_arg%>%rename_all(tolower),by = c("subjid"))%>%
  mutate(community = "buenos_aires")%>%
  distinct(subjid, trialnr, .keep_all = TRUE)
```

@@

```{r}
# quality checks

# range of click distance: min = 0; max = 1920
range(abs(tidy_data_ind$clickDistFromTargetCenterX)) #

# number of trials: everyone should have more than 4 trials.
tidy_data_ind%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)

@@

```{r }
raw_demographics_ind <- read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/india/Gafo_Corrected.xlsx", sheet = 1)

tidy_demographics_ind <- raw_demographics_ind %>% 
  mutate(
    test_date = as.Date(as.character(test_date), format = "%Y%m%d"),
    birth_date = as.Date(as.character(birth_date), format = "%Y%m%d"),
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
  )  %>%
  select(-c(test_date, birth_date, comment))%>%
  filter(!is.na(ageinyears))%>%
  rename(subjid = id)

@@

```{r}
# quality checks

# check for typos in subject names
tidy_demographics_ind%>%
  filter(!subjid %in% tidy_data_ind$subjID)

# range of ages: should not be below 2.5
range(tidy_demographics_ind$ageinyears)

# screen and touchscreen should only be 0 or 1 or NA
unique(tidy_demographics_ind$screen) 
unique(tidy_demographics_ind$touchscreen)

# children should at least be 1 (the tested child) 
tidy_demographics_ind%>%filter(children < 1)
# household should at least be 2 (the tested child and one adult) 
tidy_demographics_ind%>%filter(household < 2) 
# household should be larger than children
tidy_demographics_ind%>%filter(children >= household) 
# youngerchildren should be fewer than children
tidy_demographics_ind%>%filter(younger_children >= children)

exclude_ind <- c(tidy_demographics_ind%>%filter(children >= household) %>% pull(subjid),
                 tidy_demographics_ind%>%filter(younger_children >= children)%>% pull(subjid))

@@

```{r}
data_ind <- tidy_demographics_ind%>%
  filter(!subjid %in%exclude_ind)%>%
  left_join(tidy_data_ind%>%rename_all(tolower),by = c("subjid"))%>%
  mutate(community = "india")%>%
  distinct(subjid, trialnr, .keep_all = TRUE)
```

@@

```{r}
# quality checks

# range of click distance: min = 0; max = 1920
range(abs(tidy_data_nz$clickDistFromTargetCenterX)) #

# number of trials: everyone should have more than 4 trials.
tidy_data_nz%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)

```{r demographics}
raw_demographics_nz <- bind_rows(
  read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/new_zealand/gafo-cc-new-zealand-participants.xlsx", sheet = 1)
  )%>%
  filter(id != "NZ000001")

@@

```{r}
# quality checks

# check for typos in subject names
tidy_demographics_nz%>%
  filter(!subjid %in% tidy_data_nz$subjID)

# range of ages: should not be below 2.5
range(tidy_demographics_leipzig$ageinyears)

# screen and touchscreen should only be 0 or 1 or NA
unique(tidy_demographics_leipzig$screen) 
unique(tidy_demographics_leipzig$touchscreen)

# children should at least be 1 (the tested child) 
tidy_demographics_leipzig%>%filter(children < 1)
# household should at least be 2 (the tested child and one adult) 
tidy_demographics_leipzig%>%filter(household < 2) 
# household should be larger than children
tidy_demographics_leipzig%>%filter(children >= household) 
# youngerchildren should be fewer than children
tidy_demographics_leipzig%>%filter(younger_children >= children) 
```

```{r}
data_nz <- tidy_demographics_nz%>%
  left_join(tidy_data_nz%>%rename_all(tolower),by = c("subjid"))%>%
  distinct(subjid, trialnr, .keep_all = TRUE)
```

@@

```{r}
# quality checks

# range of click distance: min = 0; max = 1920
range(abs(tidy_data_tur$clickDistFromTargetCenterX)) #

# number of trials: everyone should have more than 4 trials.
tidy_data_tur%>%group_by(subjID)%>%filter(voiceover == F, trialType == "test")%>%summarise(n = n())%>%filter(n<5)

@@

```{r}
# quality checks

# check for typos in subject names
tidy_demographics_tur%>%
  filter(!subjid %in% tidy_data_tur$subjID)

# range of ages: should not be below 2.5
range(tidy_demographics_tur$ageinyears)

# screen and touchscreen should only be 0 or 1 or NA
unique(tidy_demographics_tur$screen) 
unique(tidy_demographics_tur$touchscreen)

# children should at least be 1 (the tested child) 
tidy_demographics_tur%>%filter(children < 1)
# household should at least be 2 (the tested child and one adult) 
tidy_demographics_tur%>%filter(household < 2) 
# household should be larger than children
tidy_demographics_tur%>%filter(children >= household) 
# youngerchildren should be fewer than children
tidy_demographics_tur%>%filter(younger_children >= children) 
```
